\newpage
\addcontentsline{toc}{chapter}{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ} % это будет отображаться в содержании
\renewcommand{\bibsection}{\centering\textbf{\large СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}} % смена названия библиографии по умолчанию
%\bibliographystyle{biblio/gost2008n}
\bibliographystyle{plain}
%\bibliography{biblio/biblio}

\begin{thebibliography}{9}

\bibitem{prip2023}
Novikov, A. A. Prediction of protein-protein interaction with cosine matrices / A. A. Novikov, A. V. Tuzikov, A. V. Batyanovskii // Pattern Recognition and Information Processing (PRIP'2023) : Proceedings of the 16th International Conference, October 17–19, 2023, Minsk, Belarus / United Institute of Informatics Problems of the National Academy of Sciences of Belarus. – Minsk, 2023. – P. 258–263.

\bibitem{fully_conv}
Shelhamer, E. Fully convolutional networks for semantic segmentation / E. Shelhamer, J. Long // IEEE – 2015. – P. 1-12.

\bibitem{symmetry}
Exploring protein symmetry at the RCSB Protein Data Bank / J. Duarte [et al] // Emerging Topics in Life Sciences. – 2022. – P. 1-13.

\bibitem{vreven}
Vreven, T. Integrating atom-based and residue-based scoring functions for protein–protein docking / T.Vreven, H. Hwang, Z. Weng // Protein Sci. – 2011. – P. 1-11.

\bibitem{AF2}
Highly accurate protein structure prediction with AlphaFold / J. Jumper [et al] // Nature. – 2021. – P. 1-16.

\bibitem{AFM}
Protein complex prediction with AlphaFold-Multimer / R. Evans [et al] // DeepMind. – 2021. – P. 1-25.

\bibitem{AF3}
Accurate structure prediction of biomolecular interactions with AlphaFold 3 / J. Abramson [et al] // Nature. -- 2024. --P. 493-517.

\bibitem{AF_followers}
FastFold: Reducing AlphaFold Training Time from 11 Days to 67 Hours / S. Cheng [et al] // arXiv. – 2023. – P. 1-13.

\bibitem{andras}
Andras, S. Template-based structure modeling of protein-protein interactions / S. Andras, Y. Zhang // Curr Opin Struct Biol. – 2014. – P. 1-24.

\bibitem{deep_methods}
Deep Learning for Protein–Protein Interaction Site Prediction / R. Arian [et al.] // Methods Mol Biol. – 2021. – P. 1-26.

\bibitem{hang}
Hang, Y. Protein surface representation and analysis by dimension reduction / Y. Hang, R. Quershi, A. Sacan // Proteome Science. – 2012. – P. 1-13.

\bibitem{sverrisson}
Fast end-to-end learning on protein surfaces / F. Sverrisson [et al] // bioRxiv. – 2020. – P. 1-11.

\bibitem{guo}
Prediction of inter-chain distance maps of protein complexes with 2D attentionbased deep neural networks / Z. Guo [et al] // University of Missouri. – 2022. – P. 1-13.

\bibitem{hadarovich}
Хадарович, А. Ю. Алгоритмы моделирования димерных белковых комплексов / А. Ю. Хадарович // ОИПИ НАН. – 2020. – P. 1-100.

\bibitem{kufareva}
Kufareva, I. Methods of protein structure comparison / I. Kufareva, R. Abagyan // Methods Mol Biol. – 2012. – P. 1-30.

\bibitem{bradley}
Bradley, A. The use of the area under the ROC curve in the evaluation of machine learning algorithms / A. P. Bradley // Pattern Recognition. – 1997. – P. 1145-1159.

\bibitem{basu}
Basu, S. DockQ: A Quality Measure for Protein-Protein Docking Models / S. Basu, B. Wallner // PLoS ONE. – 2016. – P. 1-9.

\bibitem{zhu}
Evaluation of AlphaFold-Multimer prediction on multi-chain protein complexes / W. Zhu [et al] // Bioinformatics. -- 2023. -- P. 1-7.

\bibitem{field_theory}
Богуш, А.А. Введение в теорию классических полей / А. А. Богуш, Л. Г. Мороз. -- Изд. 2-е. -- М.: Едиториал УРСС, 2004. -- 384 с.

\bibitem{adam}
Kingma, D. Adam: A Method for Stochastic Optimization / D. Kingma, J. Ba // arXiv. -- 2017. -- P. 1-15.

\bibitem{evol_methods}
Eiben, A. Introduction to Evolutionary Computing / A.E. Eiben, J.E. Smith. -- 2nd ed. -- Berlin : Springer, 2015. -- XII, 287 p.

\bibitem{resnet}
Deep Residual Learning for Image Recognition / H. Kaiming [et al] // arXiv. – 2015. – P. 1-12.

\bibitem{batchnorm}
Ioffe, S. Batch Normalization: Accelerating Deep Network Training by Reducing Internal Covariate Shift / S. Ioffe, C. Szegedy // arXiv. – 2015. – P. 1-11.

\bibitem{unet}
Ronnenberger, O. U-Net: Convolutional Networks for Biomedical Image Segmentation / O. Ronnenberger, P. Fisher, T. Brox // arXiv. – 2015. – P. 1-8.

\bibitem{attention_all_you_need}
Attention Is All You Need / A. Vaswani [et al] // arXiv. – 2015. P. 1-15.

\end{thebibliography}